---
title: "Pilot analysis"
output: pdf_document
author: "Mattias Agerberg and Marcus Tannenberg"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)

df <- rio::import("data/survey-data.csv")

```
## General

### Attentives and inattentives

How many pass the imc/s?
```{r}
#pass imc_1 (click next)
df %>% group_by(imc_1) %>% summarise(N=n())

#pass imc_2_1 (chose middle option)
df %>% group_by(imc_2_1) %>% summarise(N=n())

#pass imc_2_2 (two greater than one)
df %>% group_by(imc_2_2) %>% summarise(N=n())

#how many are attentive in our sample?
df %>% group_by(attentive_imc) %>% summarise(N=n())

```

### Survey time

How much time do respondents spend on the survey?
```{r}
df %>% 
  ggplot(aes(x=time_spent)) +
  geom_density()
```

How about difference between attentive and innatentive?

```{r}
df %>% 
  ggplot(aes(x=time_spent, fill = attentive_imc)) +
  geom_density()
```
```

### IP-duplicates
There should be a block so that same ip-number can't take survey twice, but lets double check that:

```{r}
unique(df$IPAddress, na.rm=TRUE)
```

### Geo-distribution

```{r}
#install.packages("mapview")
library(mapview)
library(sf)

#create sf object
map <- df_test %>% 
  st_as_sf(coords = c("lng", "lat")) 

#set projection
st_crs(map) <- st_crs(4326)

mapview::mapview(map)

```

## List design

### Ceeling and floor issues
lets check that that we don't have too many 0 and max-values
```{r}
df %>% 
select(a_control:e_treatment) %>% 
  gather() %>% 
  ggplot(aes(x=value)) +
  geom_histogram() +
  facet_wrap(~key)
```

lets see if its better when we drop innatentives:
```{r}
df %>% 
filter(attentive_imc = "attentive") %>% 
select(a_control:e_treatment) %>% 
  gather() %>% 
  ggplot(aes(x=value)) +
  geom_histogram() +
  facet_wrap(~key)
```


### lets look at our simple DIM:s
First, can we recover the A estimand of 1/4 and B estimand of 1/6?
Second, are we getting the expected direction on C to E? 

```{r}
df %>% select(a_control:e_treatment, c_direct, d_direct, e_direct) %>% 
  summarise_all(mean, na.rm=TRUE) %>% 
  mutate(a_dim = a_treatment - a_control, 
         b_dim = b_treatment - b_control, 
         b_dim_placebo = b_treatment - b_placebo,
         c_dim = c_treatment - c_control,
         d_dim = d_treatment - d_control,
         e_dim = e_treatment - c_control,
         e_dim = e_treatment - c_control,
         e_dim_placebo = e_treatment - e_placebo,
         c_est = c_direct - c_dim, 
         d_est = d_direct - d_dim, 
         e_est = e_direct - e_dim, 
         e_est_placebo = e_direct - e_dim_placebo) %>% 
  select(a_dim:e_est_placebo)
```

how about when only using attentive respondents? Are we better at recovering A and B? 
```{r}
df %>% 
  filter(attentive_imc == "attentive") %>% 
  select(a_control:e_treatment, c_direct, d_direct, e_direct) %>% 
  summarise_all(mean, na.rm=TRUE) %>% 
  mutate(a_dim = a_treatment - a_control, 
         b_dim = b_treatment - b_control, 
         b_dim_placebo = b_treatment - b_placebo,
         c_dim = c_treatment - c_control,
         d_dim = d_treatment - d_control,
         e_dim = e_treatment - c_control,
         e_dim = e_treatment - c_control,
         e_dim_placebo = e_treatment - e_placebo,
         c_est = c_direct - c_dim, 
         d_est = d_direct - d_dim, 
         e_est = e_direct - e_dim, 
         e_est_placebo = e_direct - e_dim_placebo) %>% 
  select(a_dim:e_est_placebo)
```

How about our pRMSE for a and b? 
```{r}

#here's our function

prmse <- function(estimand, treatment, control) {
  sqrt( 
    (var(treatment, na.rm=TRUE) + var(control, na.rm=TRUE))
    + (estimand - ((mean(treatment, na.rm=TRUE) - mean(control, na.rm=TRUE))^2))
    )
}

prmse_a <-  prmse(estimand = .25, df$a_treatment, df$a_control) 

#don't know what fucked up the function but have to use base r
df_att <- df %>% filter(attentive_imc == "attentive")

prmse_a_att <-  prmse(estimand = .25, df_att$a_treatment, df_att$a_control)

prmse_a
prmse_a_attentives

# lets do that for B

prmse_b <- prmse(estimand = (1/6), df$b_treatment, df$b_control) 
prmse_b_placebo <- prmse(estimand = (1/6), df$b_treatment, df$b_placebo) 

# and for attentives only

prmse_b_att <- prmse(estimand = (1/6), df_att$b_treatment, df_att$b_control) 
prmse_b_placebo_att <- prmse(estimand = (1/6), df_att$b_treatment, df_att$b_placebo) 

prmse_b
prmse_b_placebo
prmse_b_att
prmse_b_placebo_att

```



### Placebo items
did the placebo item get aprox 0 agreement? I.e we don't want 1:s here

```{r}
df %>% group_by(placebo_direct) %>% summarise(N=n())
```

do we get fewer oned when dropping inattentives?
```{r}
df %>% filter(attentive_imc = "attentive") %>% 
group_by(placebo_direct) %>% summarise(N=n())
```


